A Spatial AR System for Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-11 paper/elsarticle/elsarticle-template.tex
Update elsarticle-template.tex

Keystone correction for planar scenes can be carried out using a 2D homography \cite{Hartley2004}---an invertible transformation that preserves colinearity---and is ultimately the approach we take as well. One approach to calibrating a projector-camera system using a homography reduces to automatically establishing keypoint matches between the image to be projected in the projector's image plane and the projected image in the camera's image plane, and then to use those matches to automatically compute the homography that warps the one image to the other \cite{sukthankar2001smarter}. While such an approach could be extended to enable placement to multiple locations in accordance with a steerable mirror, using keypoint matches alone does not enable reasoning about the target dimensions of augmentations in metric terms.

>>>>

Keystone correction for planar scenes can be carried out using a 2D homography \cite{Hartley2004}---an invertible transformation that preserves colinearity---and is ultimately the approach we take as well. One approach to calibrating a projector-camera system using a homography reduces to automatically establishing keypoint matches between the image to be projected in the projector's image plane and the projected image in the camera's image plane, and then using those matches to automatically compute the homography that warps the one image to the other \cite{sukthankar2001smarter}. While such an approach could be extended to enable placement to multiple locations in accordance with a steerable mirror, using keypoint matches alone does not enable reasoning about the target dimensions of augmentations in metric terms.
